---
title: "R Code for Finding Full Factorial"
date: "`r Sys.Date()`"
author: Jung-Han (Hank) Wang jwang@knights.ucf.edu
output:
  rmdformats::readthedown:
    highlight: kate
---
```{r 1,echo=FALSE}
setwd("H:/Cloud Storage/Dropbox/Life long study/Ph.D/Lecture/2016 Spring/Experimental Design/R project/Experimental Design/Full Factorial")
options(max.print=16)
```

```{r knitr_init, echo=FALSE, cache=FALSE,warning=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75")
opts_chunk$set(echo=TRUE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)

options(max.print=100)
```

## Get the Tool

Using the code written by Josh. He had suggested to get mgcv packge installed and load package mgcv.

I failed at running the function `uniquecombs` in mgcv package at beginning. But after I updated mgcv package using the code indicated below.
I was able to get it running on Windows, MAC, and Ubuntu.
```{r 2, eval=FALSE}
## Install mgcv package, be default R will install from CRAN
install.packages("mgcv")
## Load mgcv package
library(mgcv)
```

## Load the data

If the file was put in the same location. It should be fine loading the data using the sample code; otherwise, please check the next section.
The sample data I used can be found using the link here.

__Sample File Download Link__ <https://goo.gl/OOLrCK>

``` {r 3}
x <- read.table(file="design.txt", sep="\t", header=TRUE)
```

A succefully loaded data looks like this:
```{r 10}

x
```

If there is problem loading the data. Simply replacing `"design.txt"` with the full path. For example: 

- In MAC: `/Users/experimental_design/....../design.txt`
- In Windows: `c:/Spring2016/experimental_design/....../design.txt`

## Rename the Column

Using this code.

```{r 4}
colnames(x) <- LETTERS[1:ncol(x)]
```

## Generate an Empty Storage

```{r 5}
unq <- numeric(length(combn(x,log2(nrow(x)),simplify=FALSE)))
```

## Make all Combinations

```{r 6}
cmb <- combn(x,log2(nrow(x)),simplify=FALSE)
```

## Check the Number of Unique Rows

Check how many unique rows in each possible combinations and store the number of unique unique rows to the empty storage `unq`

```{r 7}
for (i in 1:length(combn(x,log2(nrow(x)),simplify=FALSE))){
	unq[i] <- nrow(uniquecombs(cmb[i]))
	}
unq                 # number of unique rows for each combination
```

## Get Result

```{r 8}
full.fact<-cmb[unq==nrow(x)]   # full factorial in . . .
full.fact

```

## Alphabet only Results

Using the result generated in the previous section. The alphabet representation result can be retrieved using the code:

``` {r 9}
## I added couple line to display the result
full.fact.alpha<-sapply(1:length(full.fact),function(x)colnames(full.fact[[x]]))
## Rotate and change to data frame
data.frame(t(full.fact.alpha))

```

## Appendix R code

Download the R code (by Josh forked by Hank) <https://goo.gl/ZF64oi>

```{r all-code, ref.label=paste0(c(2:9)), echo=TRUE, eval=FALSE, tidy.opts=list(keep.blank.line=T)}
```